Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/revisited.tex
updates to paper
update section labels and fixup appendix
Minor edit.

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}

\section{Performance in Isolation, Revisited}\label{section:revisited}

@@

\begin{figure}[ht]
\includegraphics[scale=0.35]{figures/rep_distribution_nih}
\caption{Distribution of reputation scores for Needle-in-Haystack at $t=500$ (smoothed using a kernel density estimate)}
\label{rep_dist_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the reputation distribution at $t = 500$}}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[scale=0.35]{figures/ts_dg_rep_diff_nih}
\caption{Distribution of reputation difference $\TS-\DG$ for  Needle-in-Haystack
% at $t = 500, 1000, 2000$ AS: this is redundant, and it saves a line :).
(smoothed via a kernel density estimate)}
\label{ts_dg_rep_diff_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the difference in reputation between $\TS$ and $\DG$ across $t$}}
\end{figure}

>>>>

\documentclass[../competing_bandits_with_appendix.tex]{subfiles}
\begin{document}

\section{Performance in Isolation, Revisited}\label{sec:revisited}

@@

\begin{figure}[ht]
\includegraphics[scale=0.35]{figures/rep_distribution_nih}
\caption{Reputation scores for Needle-in-Haystack at $t=500$ (smoothed using a kernel density estimate)}
\label{rep_dist_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the reputation distribution at $t = 500$}}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[scale=0.35]{figures/ts_dg_rep_diff_nih}
\caption{Reputation difference $\TS-\DG$ for  Needle-in-Haystack
% at $t = 500, 1000, 2000$ AS: this is redundant, and it saves a line :).
(smoothed using a kernel density estimate)}
\label{ts_dg_rep_diff_nih}
%\caption*{\tiny{The plots contain a kernel density estimate of the difference in reputation between $\TS$ and $\DG$ across $t$}}
\end{figure}
